Relating two Abstractions for Formal Array Languages

### 2014-04-11 paper.tex
Create a figure for the rosetta table
Wibble
Removed a statement about MoA types as it used undefined functions

When it comes to types MoA keeps things very simple. There is just one
type, arrays.  Scalars are arrays;  their shape is the empty vector. Consequently, we have the identity given any array, $\xi$
\[( \iota (\rho \xi)  )\psi \xi \equiv \xi\]
That is, given an array's shape, all indices can be generated to index the entire array.
% scalars are arrays from an MoA and Psi Calculus perspective.

@@

\begin{tabular}{|@{}l|l@{}|}
\hline
MoA & Feldspar
\\
\hline
δ & \verb!dim . extent!
\\
ρ & \verb!extent!
\\
ιξⁿ & generalized \verb!enumFromTo!
\\
ψ & generalized \verb!index!
\\
rav & -- flattens to a one-dimensional array
\\
γ & \verb!toIndex!
\\
γ' & \verb!fromIndex!
\\
$s \: \hat{ρ} \: ξ$ & \verb!reshape!
\\
π x & \verb!product!
\\
τ & \verb!size!
\\
++ & ++
\\
ξ₁ f ξ₂ & \verb!zipWith f! ξ₁ ξ₁
\\
σ f ξ & \verb!map f! ξ
\\
ξ f σ & \verb!map f! ξ
\\
$\bigtriangleup$ & \verb!take!
\\
$\bigtriangledown$ & \verb!drop!
\\
$op^{red}$ & \verb!fold op!
\\
Φ & \verb!reverse!
\\
Θ & \verb!rotate!
\\
$\varobslash$ & generalized \verb!transpose!
\\
$f Ω_d ξ$ & -- Apply $f$ along the dimension $d$ of $ξ$
\\
\hline
\end{tabular}

>>>>

When it comes to types MoA keeps things very simple. There is just one
type, arrays.  Scalars are arrays;  their shape is the empty vector.

% I've removed this statement because \rho is not defined in the paper
%% Consequently, we have the identity given any array, $\xi$
%% \[( \iota (\rho \xi)  )\psi \xi \equiv \xi\]
%% That is, given an array's shape, all indices can be generated to index the entire array.
% scalars are arrays from an MoA and Psi Calculus perspective.

@@

Figure \ref{fig:rosetta} gives a translation between function names
used in MoA and Pull arrays.

\begin{figure}
\begin{center}
\begin{tabular}{|@{}l|l@{}|}
\hline
MoA & Feldspar
\\
\hline
δ & \verb!dim . extent!
\\
ρ & \verb!extent!
\\
ιξⁿ & generalized \verb!enumFromTo!
\\
ψ & generalized \verb!index!
\\
rav & -- flattens to a one-dimensional array
\\
γ & \verb!toIndex!
\\
γ' & \verb!fromIndex!
\\
$s \: \hat{ρ} \: ξ$ & \verb!reshape!
\\
π x & \verb!product!
\\
τ & \verb!size!
\\
++ & ++
\\
ξ₁ f ξ₂ & \verb!zipWith f! ξ₁ ξ₁
\\
σ f ξ & \verb!map f! ξ
\\
ξ f σ & \verb!map f! ξ
\\
$\bigtriangleup$ & \verb!take!
\\
$\bigtriangledown$ & \verb!drop!
\\
$op^{red}$ & \verb!fold op!
\\
Φ & \verb!reverse!
\\
Θ & \verb!rotate!
\\
$\varobslash$ & generalized \verb!transpose!
\\
$f Ω_d ξ$ & -- Apply $f$ along the dimension $d$ of $ξ$
\\
\hline
\end{tabular}
\end{center}
\caption{A correspondence between functions in MoA and Pull arrays}
\label{fig:rosetta}
\end{figure}
